### 2015-04-14 LCAforActiveSonarImaging/lca.tex
More on LCA

In active sonar array imaging, an acoustic wave is transmitted and the received echoes are usually recorded using an array of sensors. Each of these may be independently delayed and weighted such that signals emanating from directions of interest are added constructively, while noise and interference from other directions add destructively. Additionally, a window may be applied to the sensor channels to further adjust the arrays spatial response. This process is known as beamforming.% The process of combining the signals from each sensor is known as beamforming.

>>>>

Most modern active sonar imaging systems are usually far better at resolving details in range than in the angular direction. This is because it is relatively cheap and easy to collect a long and well sampled temporal representation of the incoming wavefield, but hard to do so spatially. It would require a very large array with a lot of sensors, which is costly, complex and impractical. Alternatively, a larger array can be synthesized from several successive pings recorded by a smaller physical array using a technique called synthetic aperture sonar (SAS). Unfortunately, not many of these systems exist due to the difficulty of navigating with sufficiently high precision under water.

It would be more convenient to avoid 
Hence, if the angular resolution can be improved by  the angular resoliutio
Since A solution that is more convenient, cost-effective and simple solution would be to

than itof to collect information from an extended part of the incoming wave in time it is easier to sample the incoming wavefield both the wavefield is better the angular resolution is usually far inferior to the The quality of active sonar imaging systems are

Improving the angular resulution of active sonar systems are 
In general the 
In modern active sonar imaging systems it is generally harder to obtain sufficient is to transmit and receive wideband acustic pulses using multi-sensor arrays. and process their record the backscattered wavefield using an array of hydrophones.  Through a coherent combination of the sensor data these

In active sonar array imaging, an acoustic wave is transmitted and the received echoes are usually recorded using an array of sensors. Each of these may be independently delayed and weighted such that signals emanating from directions of interest are added constructively, while noise and interference from other directions add destructively. Additionally, a window may be applied to the sensor channels to further adjust the array's spatial response. This process is known as beamforming.% The process of combining the signals from each sensor is known as beamforming.

### 2015-04-14 ThesisJo/derivations.tex
More on LCA

>>>>

Tommelfingerregel for styring
- 1/2 av rektangulær for punkter
- 1/2 Hamming/Kaiser for skarpe transisjoner

- Omtrent samme beta i transisjoner
- Samme beta i spekkel/highlight
- Annen beta i skygge

Bildeparametre:
- Oppløsning
- Kontrast.
- Dynamisk område.
- I sonar er spekkel tekstur! Vi kan tillate en undertrykking av den, men ønsker forholdsvis lik spekkelstatistikk.
- Temporal and spatial shift variance. Et punkt burde avbildes med omtrent samme amplitude uansett hvor det er i bildet.
- Sensitivitet
- Steered response.
- Coherence
- Qualitative assessment

Hvor mange trenger vi.
1. Brute force. Tester alle kombinasjoner av
   - Oversampling
   - Beta
   - Styring
2. Hva det koker ned til.
   - Oversampling. Virker som om 2*M er en god regel, trenger litt mer om vi tillater mye styring.
   - Beta. Holder med 3-6. Kan regnes anaAnalytisk
   - Styring. Desto mer styring, desto mer agressiv beamforming. Burde ikke styre mer enn av vi får litt variasjon av nullpunkt, men med liten skift-invarians i amplitide.

Sammenlignet med MVDR
- Hvorfor trenger vi ikke subarray / tidsmidling?
- MVDR er ``for'' adaptiv. Selv med 1-gain rett frem kan signalet derfra kansellers. Subarray midling hjelper mot dette, men tar ned oppløsningen. LCA har ikke frihet til å velge amplitude/phase kombinasjoner som tillater signalkansellering, og det viser seg at vi da ikke trenger å midle for å oppnå ønsket resultat.
